---
title: "2YP_Analysis_AERA"
author: "Jessa Henderson"
date: "1/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(plyr)
library(dplyr)
library(readr)
library(tidyr)
library(likert)
library(ggplot2)
```

## Data Preprocessing: Loading the Data
A CSV file from the survey was uploaded into R Studio for preprocessing and cleaning.

Prior to cleaning, the dataset contained 93 observations and 73 variables

```{r Setup, echo=TRUE}
#Load CSV
CFResearch_Full <- read.csv('2YP_Data.csv', header = TRUE)

#Convert to dataframe
CFResearch_df <- data.frame(CFResearch_Full)

#Quick Summary of the dataframe
str(CFResearch_df)
summary(CFResearch_df)

#Create subset of data for hypothesis testing
#Includes all TAM3 and CF inventory scores. Removes demographic variables and use measured via self-reported hours.
TAM3_CF <- CFResearch_df[,c(5:11, 13:73)]

```

##Data Cleaning
Code is inefficient but goes variable by variable to ensure appropriate adjustments.
For each variable, the data was turned to a factor, removed all text, added NAs to blanks, and reversed the scale for questions that were written in the negative. 

```{r Cleaning USE, echo=FALSE}
#Cleaning  for the variable "USE"

#USE2a - use LMS to share content and documents
TAM3_CF$USE2a <- factor(TAM3_CF$USE2a, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$USE2a)
head(TAM3_CF$USE2a)

#USE2b - Use LMS gradebook
TAM3_CF$USE2b <- factor(TAM3_CF$USE2b, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$USE2b)
head(TAM3_CF$USE2b)


#USE2c - Use LMS calendar
TAM3_CF$USE2c <- factor(TAM3_CF$USE2c, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$USE2c)
head(TAM3_CF$USE2c)

#USE2d - Use LMS quiz tool
TAM3_CF$USE2d <- factor(TAM3_CF$USE2d, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$USE2d)
head(TAM3_CF$USE2d)

#USE2e - Use LMS discussion boards
TAM3_CF$USE2e <- factor(TAM3_CF$USE2e, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$USE2e)
head(TAM3_CF$USE2e)

#USE2f - Use LMS announcements
TAM3_CF$USE2f <- factor(TAM3_CF$USE2f, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$USE2f)
head(TAM3_CF$USE2f)

#USE2g - use of LMS for assignments for student submission
#Placing "NA" in blank cells 
table(TAM3_CF$USE2g)
levels(TAM3_CF$USE2g)
TAM3_CF$USE2g[TAM3_CF$USE2g == ""] <- NA
summary(TAM3_CF$USE2g)
TAM3_CF$USE2g <- factor(TAM3_CF$USE2g, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$USE2g)
head(TAM3_CF$USE2g)

#descriptive use visualization
#Create USE dataframe
USE <- subset.data.frame(TAM3_CF[1:7])
USE <- USE %>%
rename("documents" = USE2a, 
        "gradebook" = USE2b,
        "calendar" = USE2c,
        "quiz" = USE2d,
        "discussion" = USE2e,
        "announcements" = USE2f,
        "submit assignments" = USE2g)
# Create a likert object
use_likert <-  likert(USE)

# Figure 
USEPlot <- plot(use_likert, ordered = FALSE, group.order = names(USE))
#ggsave("Use.png", width = 10, height = 5)
print(USEPlot)

```

```{r Cleaning Behavioral Intent, echo=FALSE}

#BI1 - General intention to use LMS in current school year
TAM3_CF$BI1 <- factor(TAM3_CF$BI1, levels = c("1", "2", "3", "4", "5", "6", "7"))
summary(TAM3_CF$BI1)
head(TAM3_CF$BI1)
TAM3_CF$BI1 <- revalue(TAM3_CF$BI1, c("1"="strongly disagree", "2"="moderately disagree", "3"="somewhat disagree", "4"="neutral (neither agree or disagree)", "5"="somewhat agree", "6"="moderately agree", "7"="strongly agree"))

#BI2a - Intention to share content and documents
TAM3_CF$BI2a[TAM3_CF$BI2a == ""] <- NA
TAM3_CF$BI2a <- factor(TAM3_CF$BI2a, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$BI2a)
head(TAM3_CF$BI2a)

#BI2b - Intention to use LMS gradebook
TAM3_CF$BI2b[TAM3_CF$BI2b == ""] <- NA
TAM3_CF$BI2b <- factor(TAM3_CF$BI2b, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$BI2b)
head(TAM3_CF$BI2b)

#BI2c - Intention to use LMS calendar
TAM3_CF$BI2c[TAM3_CF$BI2c == ""] <- NA
TAM3_CF$BI2c <- factor(TAM3_CF$BI2c, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$BI2c)
head(TAM3_CF$BI2c)

#BI2d - Intention to use LMS quiz tool
TAM3_CF$BI2d[TAM3_CF$BI2d == ""] <- NA
TAM3_CF$BI2d <- factor(TAM3_CF$BI2d, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$BI2d)
head(TAM3_CF$BI2d)

#BI2e - Intention to use LMS discussion boards
TAM3_CF$BI2e <- factor(TAM3_CF$BI2e, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$BI2e)
head(TAM3_CF$BI2e)

#BI2f - Intention to use LMS announcements
TAM3_CF$BI2f[TAM3_CF$BI2f == ""] <- NA
TAM3_CF$BI2f <- factor(TAM3_CF$BI2f, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$BI2f)
head(TAM3_CF$BI2f)

#BI2g - Intention to use LMS for assignments for student submission
TAM3_CF$BI2g <- factor(TAM3_CF$BI2g, levels = c("strongly disagree", "moderately disagree", "somewhat disagree", "neutral (neither agree or disagree)", "somewhat agree", "moderately agree", "strongly agree"))
summary(TAM3_CF$BI2g)
head(TAM3_CF$BI2g)

#descriptive use visualization
#Create Intent dataframe
INTENT <- subset.data.frame(TAM3_CF[8:15])

INTENT <- INTENT %>%
  rename("overall" = BI1,
         "documents" = BI2a,
         "gradebook" = BI2b,
         "calendar" = BI2c,
         "quiz" = BI2d,
         "discussion" = BI2e,
         "announcements" = BI2f,
         "submit assignments" = BI2g)

# Create a likert object
intent_likert <-  likert(INTENT)

# Figure 
BIPlot <- plot(intent_likert, ylab = "Behavioral Intent", ordered = FALSE, group.order = names(INTENT))
#ggsave("Intent.png", width = 10, height = 5)
print(BIPlot)

```

```{r Cleaning Perceived Ease of Use, echo=FALSE}

#PEU1 - LMS clear & understandable
TAM3_CF$PEU1 <- as.factor(TAM3_CF$PEU1)
summary(TAM3_CF$PEU1)
TAM3_CF$PEU1 <- factor(TAM3_CF$PEU1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#PEU2 - Does not require a lot of mental effort
TAM3_CF$PEU2 <- as.factor(TAM3_CF$PEU2)
summary(TAM3_CF$PEU2)
TAM3_CF$PEU2 <- factor(TAM3_CF$PEU2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#PEU3 - Easy to use
TAM3_CF$PEU3 <- as.factor(TAM3_CF$PEU3)
summary(TAM3_CF$PEU3)
TAM3_CF$PEU3 <- factor(TAM3_CF$PEU3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#PEU4 - Easy to do what I want
TAM3_CF$PEU4 <- as.factor(TAM3_CF$PEU4)
summary(TAM3_CF$PEU4)
TAM3_CF$PEU4 <- factor(TAM3_CF$PEU4, levels = c("1", "2", "3", "4", "5", "6", "7"))

#descriptive visualization
#Create PEU dataframe
PEU <- subset.data.frame(TAM3_CF[16:19])

PEU <- PEU %>%
  rename("Clear & understandable" = PEU1,
         "Little mental effort" = PEU2,
         "Easy to use" = PEU3,
         "Easy to do what I want" = PEU4)

# Create a likert object
PEU_likert <-  likert(PEU)

# Figure 
PEUPlot <- plot(PEU_likert, ordered = FALSE, group.order = names(PEU))
#ggsave("PEU.png", width = 10, height = 5)
print(PEUPlot)

```


```{r Cleaning Perceived Usefulness, echo=FALSE}

#PU1 - Improves job performance
TAM3_CF$PU1 <- as.factor(TAM3_CF$PU1)
summary(TAM3_CF$PU1)
TAM3_CF$PU1 <- factor(TAM3_CF$PU1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#PU2 - Increases productivity
TAM3_CF$PU2 <- as.factor(TAM3_CF$PU2)
summary(TAM3_CF$PU2)
TAM3_CF$PU2 <- factor(TAM3_CF$PU2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#PU3 - Enhances job effectiveness
TAM3_CF$PU3 <- as.factor(TAM3_CF$PU3)
summary(TAM3_CF$PU3)
TAM3_CF$PU3 <- factor(TAM3_CF$PU3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#PU4 - Useful
TAM3_CF$PU4 <- as.factor(TAM3_CF$PU4)
summary(TAM3_CF$PU4)
TAM3_CF$PU4 <- factor(TAM3_CF$PU4, levels = c("1", "2", "3", "4", "5", "6", "7"))

#descriptive visualization
#Create PU dataframe
PU <- subset.data.frame(TAM3_CF[20:23])

PU <- PU %>%
  rename("Improves job performance" = PU1,
         "Increases productivity" = PU2,
         "Enhances job effectiveness" = PU3,
         "Useful" = PU4)

# Create a likert object
PU_likert <-  likert(PU)

# Figure 
PUPlot <- plot(PU_likert, ordered = FALSE, group.order = names(PU))
#ggsave("PU.png", width = 10, height = 5)
print(PUPlot)

```

```{r Cleaning Computer Self Efficacy, echo=FALSE}

#Computer self-efficacy contains numbers and text so the variable was changed to just extract the numbers. 

#CSE1 - Could use LMS if no one was around for help
TAM3_CF$CSE1 <- sub("^(\\d+).*", "\\1", TAM3_CF$CSE1)
TAM3_CF$CSE1 <- as.factor(TAM3_CF$CSE1)
TAM3_CF$CSE1[TAM3_CF$CSE1 == ""] <- NA
summary(TAM3_CF$CSE1)
TAM3_CF$CSE1 <- factor(TAM3_CF$CSE1, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"))

#CSE2 - Could use LMS if had built-in help facility
TAM3_CF$CSE2 <- sub("^(\\d+).*", "\\1", TAM3_CF$CSE2)
TAM3_CF$CSE2 <- as.factor(TAM3_CF$CSE2)
TAM3_CF$CSE2[TAM3_CF$CSE2 == ""] <- NA
summary(TAM3_CF$CSE2)
TAM3_CF$CSE2 <- factor(TAM3_CF$CSE2, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"))


#CSE3 - Could use LMS if someone showed me how first
TAM3_CF$CSE3 <- sub("^(\\d+).*", "\\1", TAM3_CF$CSE3)
TAM3_CF$CSE3 <- as.factor(TAM3_CF$CSE3)
TAM3_CF$CSE3[TAM3_CF$CSE3 == ""] <- NA
summary(TAM3_CF$CSE3)
TAM3_CF$CSE3 <- factor(TAM3_CF$CSE3, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"))

#CSE4 - could use LMS if had used similar programs before to do the same job
TAM3_CF$CSE4 <- sub("^(\\d+).*", "\\1", TAM3_CF$CSE4)
TAM3_CF$CSE4 <- as.factor(TAM3_CF$CSE4)
TAM3_CF$CSE4[TAM3_CF$CSE4 == ""] <- NA
summary(TAM3_CF$CSE4)
TAM3_CF$CSE4 <- factor(TAM3_CF$CSE4, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"))

#descriptive use visualization
#Create CSE dataframe
CSE <- subset.data.frame(TAM3_CF[24:27])

CSE <- CSE %>%
  rename("Use w/o help" = CSE1,
         "Use if help at school" = CSE2,
         "Use if showed" = CSE3,
         "Use if similar in past" = CSE4)

# Create a likert object
CSE_likert <-  likert(CSE)

# Figure 
CSEPlot <- plot(CSE_likert, ordered = FALSE, group.order = names(CSE))
#ggsave("CSE.png", width = 10, height = 5)
print(CSEPlot)
```

```{r Cleaning Perceptions of External Control, echo=FALSE}

#PEC1 - Have control over use
TAM3_CF$PEC1 <- as.factor(TAM3_CF$PEC1)
summary(TAM3_CF$PEC1)
TAM3_CF$PEC1 <- factor(TAM3_CF$PEC1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#PEC2 - Have necessary resources to use
TAM3_CF$PEC2 <- as.factor(TAM3_CF$PEC2)
summary(TAM3_CF$PEC2)
TAM3_CF$PEC2 <- factor(TAM3_CF$PEC2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#PEC3 - Easy for me to use (w/knowledge, resources & opportunities)
TAM3_CF$PEC3 <- as.factor(TAM3_CF$PEC3)
summary(TAM3_CF$PEC3)
TAM3_CF$PEC3 <- factor(TAM3_CF$PEC3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#PEC4 - Compatible with other systems
#written in negative - flipped likert scale for data analysis
TAM3_CF$PEC4 <- as.factor(TAM3_CF$PEC4)
summary(TAM3_CF$PEC4)
TAM3_CF$PEC4 <- factor(TAM3_CF$PEC4, levels = c("7", "6", "5", "4", "3", "2", "1"))

#descriptive visualization
#Create PEC dataframe
PEC <- subset.data.frame(TAM3_CF[28:31])

PEC <- PEC %>%
  rename("Control over use" = PEC1,
         "Have necessary resources" = PEC2,
         "Easy to use w/available resources" = PEC3,
         "Compatible with other systems" = PEC4)

# Create a likert object
PEC_likert <-  likert(PEC)

# Figure 
PECPlot <- plot(PEC_likert, ordered = FALSE, group.order = names(PEC))
#ggsave("Control.png", width = 10, height = 5)
print(PECPlot)

```

```{r Cleaning Perceived Enjoyment, echo=FALSE}

#ENJ1 - Use is Enjoyable
TAM3_CF$ENJ1 <- as.factor(TAM3_CF$ENJ1)
summary(TAM3_CF$ENJ1)
TAM3_CF$ENJ1 <- factor(TAM3_CF$ENJ1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#ENJ2 - Process is pleasant
TAM3_CF$ENJ2 <- as.factor(TAM3_CF$ENJ2)
summary(TAM3_CF$ENJ2)
TAM3_CF$ENJ2 <- factor(TAM3_CF$ENJ2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#ENJ3 - Fun when using
TAM3_CF$ENJ3 <- as.factor(TAM3_CF$ENJ3)
summary(TAM3_CF$ENJ3)
TAM3_CF$ENJ3 <- factor(TAM3_CF$ENJ3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#descriptive visualization
#Create ENJ dataframe
ENJ <- subset.data.frame(TAM3_CF[32:34])

ENJ <- ENJ %>%
  rename("Enjoyable" = ENJ1,
         "Pleasant" = ENJ2,
         "Fun" = ENJ3)

# Create a likert object
ENJ_likert <-  likert(ENJ)

# Figure 
ENJPlot <- plot(ENJ_likert, ordered = FALSE, group.order = names(ENJ))
#ggsave("ENJ.png", width = 10, height = 5)
print(ENJPlot)

```


```{r Cleaning Subjective Norm, echo=FALSE}

#SN1 - Influential people think I should use
TAM3_CF$SN1 <- as.factor(TAM3_CF$SN1)
summary(TAM3_CF$SN1)
TAM3_CF$SN1 <- factor(TAM3_CF$SN1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#SN2 - Important people think I should use
TAM3_CF$SN2 <- as.factor(TAM3_CF$SN2)
summary(TAM3_CF$SN2)
TAM3_CF$SN2 <- factor(TAM3_CF$SN2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#SN3 - Admin helpful
TAM3_CF$SN3 <- as.factor(TAM3_CF$SN3)
summary(TAM3_CF$SN3)
TAM3_CF$SN3 <- factor(TAM3_CF$SN3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#SN4 - School district supports LMS
TAM3_CF$SN4 <- as.factor(TAM3_CF$SN4)
summary(TAM3_CF$SN4)
TAM3_CF$SN4 <- factor(TAM3_CF$SN4, levels = c("1", "2", "3", "4", "5", "6", "7"))

#descriptive visualization
#Create SN dataframe
SN <- subset.data.frame(TAM3_CF[35:38])

SN <- SN %>%
  rename("Influential people" = SN1,
         "Important people think I should use" = SN2,
         "Admin helpful" = SN3,
         "District Supports" = SN4)

# Create a likert object
SN_likert <-  likert(SN)

# Figure 
SNPlot <- plot(SN_likert, ordered = FALSE, group.order = names(SN))
#ggsave("SN.png", width = 10, height = 5)
print(SNPlot)

```

```{r Cleaning Image, echo=FALSE}

#IMG1 - Prestige from use
TAM3_CF$IMG1 <- as.factor(TAM3_CF$IMG1)
summary(TAM3_CF$IMG1)
TAM3_CF$IMG1 <- factor(TAM3_CF$IMG1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#IMG2 - High profile from use
TAM3_CF$IMG2 <- as.factor(TAM3_CF$IMG2)
summary(TAM3_CF$IMG2)
TAM3_CF$PU2 <- factor(TAM3_CF$IMG2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#IMG3 - Use is status symbol
TAM3_CF$IMG3 <- as.factor(TAM3_CF$IMG3)
summary(TAM3_CF$IMG3)
TAM3_CF$IMG3 <- factor(TAM3_CF$IMG3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#descriptive visualization
#Create IMG dataframe
IMG <- subset.data.frame(TAM3_CF[39:41])

IMG <- IMG %>%
  rename("Use = Prestige" = IMG1,
         "Use = High Profile" = IMG2,
         "Use = Status" = IMG3)

# Create a likert object
IMG_likert <-  likert(IMG)

# Figure 
IMGPlot <- plot(IMG_likert, ordered = FALSE, group.order = names(IMG))
#ggsave("IMG.png", width = 10, height = 5)
print(IMGPlot)


```

```{r Cleaning Job Relevance, echo=FALSE}

#REL1 - Important to use for job
TAM3_CF$REL1 <- as.factor(TAM3_CF$REL1)
summary(TAM3_CF$REL1)
TAM3_CF$REL1 <- factor(TAM3_CF$REL1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#REL2 - Relevant to use for job
TAM3_CF$REL2 <- as.factor(TAM3_CF$REL2)
summary(TAM3_CF$REL2)
TAM3_CF$REL2 <- factor(TAM3_CF$REL2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#REL3 - Pertinent to job-related tasks
TAM3_CF$REL3 <- as.factor(TAM3_CF$REL3)
summary(TAM3_CF$REL3)
TAM3_CF$REL3 <- factor(TAM3_CF$REL3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#descriptive visualization
#Create REL dataframe
REL <- subset.data.frame(TAM3_CF[42:44])

REL <- REL %>%
  rename("Important for job" = REL1,
         "Relevant for job" = REL2,
         "Pertinent to job tasks" = REL3)

# Create a likert object
REL_likert <-  likert(REL)

# Figure 
RELPlot <- plot(REL_likert, ordered = FALSE, group.order = names(REL))
#ggsave("REL.png", width = 10, height = 5)
print(RELPlot)

```

```{r Cleaning Output Quality, echo=FALSE}

#OUT1 - High quality output
TAM3_CF$OUT1 <- as.factor(TAM3_CF$OUT1)
summary(TAM3_CF$OUT1)
TAM3_CF$OUT1 <- factor(TAM3_CF$OUT1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#OUT2 - Have no problem w/output quality
TAM3_CF$OUT2 <- as.factor(TAM3_CF$OUT2)
summary(TAM3_CF$OUT2)
TAM3_CF$OUT2 <- factor(TAM3_CF$OUT2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#OUT3 - Excellent results
TAM3_CF$OUT3 <- as.factor(TAM3_CF$OUT3)
summary(TAM3_CF$OUT3)
TAM3_CF$OUT3 <- factor(TAM3_CF$OUT3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#descriptive visualization
#Create OUT dataframe
OUT <- subset.data.frame(TAM3_CF[45:47])

OUT <- OUT %>%
  rename("High quality output" = OUT1,
         "No prob w/output quality" = OUT2,
         "Excellent results" = OUT3)

# Create a likert object
OUT_likert <-  likert(OUT)

# Figure 
OUTPlot <- plot(OUT_likert, ordered = FALSE, group.order = names(OUT))
#ggsave("OUT.png", width = 10, height = 5)
print(OUTPlot)

```

```{r Cleaning Result Demonstrability, echo=FALSE}

#RES11 - No difficulty communicating results to others
TAM3_CF$RES1 <- as.factor(TAM3_CF$RES1)
summary(TAM3_CF$RES1)
TAM3_CF$RES1 <- factor(TAM3_CF$RES1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#RES2 - Can communicate to others consequences of use
TAM3_CF$RES2 <- as.factor(TAM3_CF$RES2)
summary(TAM3_CF$RES2)
TAM3_CF$RES2 <- factor(TAM3_CF$RES2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#RES3 - Results are apparent to me
TAM3_CF$RES3 <- as.factor(TAM3_CF$RES3)
summary(TAM3_CF$RES3)
TAM3_CF$RES3 <- factor(TAM3_CF$RES3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#RES4 - Difficult to explain benefits 
#NEGATIVE PHRASING
TAM3_CF$RES4 <- as.factor(TAM3_CF$RES4)
summary(TAM3_CF$RES4)
TAM3_CF$RES4 <- factor(TAM3_CF$RES4, levels = c("7", "6", "5", "4", "3", "2", "1"))

#descriptive visualization
#Create RES dataframe
RES <- subset.data.frame(TAM3_CF[48:51])

RES <- RES %>%
  rename("No difficulty communicating results" = RES1,
         "Can communicate use consequences" = RES2,
         "Apparent results" = RES3,
         "Easy to explain benefits" = RES4)

# Create a likert object
RES_likert <-  likert(RES)

# Figure 
RESPlot <- plot(RES_likert, ordered = FALSE, group.order = names(RES))
#ggsave("RES.png", width = 10, height = 5)
print(RESPlot)

```

```{r Cleaning Voluntariness, echo=FALSE}

#VOL1 - Voluntary use
TAM3_CF$VOL1 <- as.factor(TAM3_CF$VOL1)
summary(TAM3_CF$VOL1)
TAM3_CF$VOL1 <- factor(TAM3_CF$VOL1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#VOL3 - Not required
TAM3_CF$VOL3 <- as.factor(TAM3_CF$VOL3)
summary(TAM3_CF$VOL3)
TAM3_CF$VOL3 <- factor(TAM3_CF$VOL3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#VOL2 - Supervisor does not require use
TAM3_CF$VOL2 <- as.factor(TAM3_CF$VOL2)
summary(TAM3_CF$VOL2)
TAM3_CF$VOL2 <- factor(TAM3_CF$VOL2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#descriptive visualization
#Create VOL dataframe
VOL <- subset.data.frame(TAM3_CF[52:54])

VOL <- VOL %>%
  rename("Voluntary use" = VOL1,
         "Use not required" = VOL3,
         "Supervisor doesn't require" = VOL2)

# Create a likert object
VOL_likert <-  likert(VOL)

# Figure 
VOLPlot <- plot(VOL_likert, ordered = FALSE, group.order = names(VOL))
#ggsave("VOL.png", width = 10, height = 5)
print(VOLPlot)

```


```{r Cleaning Computer Playfulness, echo=FALSE}

#CPLAY1 - Characterize yourself as spontaneous with computers
TAM3_CF$CPLAY1[TAM3_CF$CPLAY1 == ""] <- NA
TAM3_CF$CPLAY1 <- factor(TAM3_CF$CPLAY1, levels = c("Strongly Disagree", "Moderately Disagree", "Somewhat Disagree", "Neutral (neither agree or disagree)", "Somewhat Agree", "Moderately Agree", "Strongly Agree"))
summary(TAM3_CF$CPLAY1)
head(TAM3_CF$CPLAY1)

#CPLAY2 - Characterize yourself as creative with computers
TAM3_CF$CPLAY2[TAM3_CF$CPLAY2 == ""] <- NA
TAM3_CF$CPLAY2 <- factor(TAM3_CF$CPLAY2, levels = c("Strongly Disagree", "Moderately Disagree", "Somewhat Disagree", "Neutral (neither agree or disagree)", "Somewhat Agree", "Moderately Agree", "Strongly Agree"))
summary(TAM3_CF$CPLAY2)
head(TAM3_CF$CPLAY2)

#CPLAY3 - Characterize yourself as playful with computers
TAM3_CF$CPLAY3[TAM3_CF$CPLAY3 == ""] <- NA
TAM3_CF$CPLAY3 <- factor(TAM3_CF$CPLAY3, levels = c("Strongly Disagree", "Moderately Disagree", "Somewhat Disagree", "Neutral (neither agree or disagree)", "Somewhat Agree", "Moderately Agree", "Strongly Agree"))
summary(TAM3_CF$CPLAY3)
head(TAM3_CF$CPLAY3)

#CPLAY4 - Characterize yourself as unoriginal with computers
#NEGATIVE phrasing so swapping order of factors/likert scale numbers
TAM3_CF$CPLAY4[TAM3_CF$CPLAY4 == ""] <- NA
TAM3_CF$CPLAY4 <- factor(TAM3_CF$CPLAY4, levels = c("Strongly Agree", "Moderately Agree", "Somewhat Agree", "Neutral (neither agree or disagree)", "Somewhat Disagree", "Moderately Disagree", "Strongly Disagree"))
summary(TAM3_CF$CPLAY4)
head(TAM3_CF$CPLAY4)

PLAYFUL <- subset.data.frame(TAM3_CF[55:58])

PLAYFUL <- PLAYFUL %>%
  rename("spontaneous" = CPLAY1,
         "creative" = CPLAY2,
         "playful" = CPLAY3,
         "original" = CPLAY4)

# Create a likert object
playful_likert <-  likert(PLAYFUL)

# Figure 
PLAYPlot <- plot(playful_likert, ordered = FALSE, group.order = names(PLAYFUL))
#ggsave("PLAY.png", width = 10, height = 5)
print(PLAYPlot)

```

```{r Cleaning Computer Anxiety, echo=FALSE}
#High anxiety = high score

#CANX1 - Do not scare me (REVERSE)
TAM3_CF$CANX1 <- as.factor(TAM3_CF$CANX1)
summary(TAM3_CF$CANX1)
TAM3_CF$CANX1 <- factor(TAM3_CF$CANX1, levels = c("7", "6", "5", "4", "3", "2", "1"))

#CANX2 - makes me nervous
TAM3_CF$CANX2 <- as.factor(TAM3_CF$CANX2)
summary(TAM3_CF$CANX2)
TAM3_CF$CANX2 <- factor(TAM3_CF$CANX2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#CANX3 - make me uncomfortable
TAM3_CF$CANX3 <- as.factor(TAM3_CF$CANX3)
summary(TAM3_CF$CANX3)
TAM3_CF$CANX3 <- factor(TAM3_CF$CANX3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#CANX4 - make me feel uneasy
TAM3_CF$CANX4 <- as.factor(TAM3_CF$CANX4)
summary(TAM3_CF$CANX4)
TAM3_CF$CANX4 <- factor(TAM3_CF$CANX4, levels = c("1", "2", "3", "4", "5", "6", "7"))

#descriptive visualization
#Create CANX dataframe
ANXIETY <- subset.data.frame(TAM3_CF[59:62])

ANXIETY <- ANXIETY %>%
  rename("Scared" = CANX1,
         "Nervous" = CANX2,
         "Uncomfortable" = CANX3,
         "Uneasy" = CANX4)

# Create a likert object
ANX_likert <-  likert(ANXIETY)

# Figure 
ANXPlot <- plot(ANX_likert, ordered = FALSE, group.order = names(ANXIETY))
#ggsave("ANX.png", width = 10, height = 5)
print(ANXPlot)


```

```{r Cleaning Change Fatigue, echo=TRUE}

#CF1 - Too many change initiatives
TAM3_CF$CF1 <- as.factor(TAM3_CF$CF1)
summary(TAM3_CF$CF1)
TAM3_CF$CF1 <- factor(TAM3_CF$CF1, levels = c("1", "2", "3", "4", "5", "6", "7"))

#CF2 - Tired of tech changes
TAM3_CF$CF2 <- as.factor(TAM3_CF$CF2)
summary(TAM3_CF$CF2)
TAM3_CF$CF2 <- factor(TAM3_CF$CF2, levels = c("1", "2", "3", "4", "5", "6", "7"))

#CF3 - Overwhelming amount of changes
TAM3_CF$CF3 <- as.factor(TAM3_CF$CF3)
summary(TAM3_CF$CF3)
TAM3_CF$CF3 <- factor(TAM3_CF$CF3, levels = c("1", "2", "3", "4", "5", "6", "7"))

#CF4 - Asked to change tech too much
TAM3_CF$CF4 <- as.factor(TAM3_CF$CF4)
summary(TAM3_CF$CF4)
TAM3_CF$CF4 <- factor(TAM3_CF$CF4, levels = c("1", "2", "3", "4", "5", "6", "7"))

#CF5 - Always being asked to change
TAM3_CF$CF5 <- as.factor(TAM3_CF$CF5)
summary(TAM3_CF$CF5)
TAM3_CF$CF5 <- factor(TAM3_CF$CF5, levels = c("1", "2", "3", "4", "5", "6", "7"))

#CF6 - like to see period of stability before next tech change
TAM3_CF$CF6 <- as.factor(TAM3_CF$CF6)
summary(TAM3_CF$CF6)
TAM3_CF$CF6 <- factor(TAM3_CF$CF6, levels = c("1", "2", "3", "4", "5", "6", "7"))

#descriptive visualization
#Create CF dataframe
CF <- subset.data.frame(TAM3_CF[63:68])

CF <- CF %>%
  rename("Too many change initiatives" = CF1,
         "Tired of change" = CF2,
         "Overwhelming amount of change" = CF3,
         "Asked to change too much" = CF4,
         "Always asked to change" = CF5,
         "Want stability" = CF6)

# Create a likert object
CF_likert <-  likert(CF)

# Figure 
CFPlot <- plot(CF_likert, ordered = FALSE, group.order = names(CF))
#ggsave("CF.png", width = 10, height = 5)
print(CFPlot)
```


```{r Compiling Mean Composite Variable Scores, echo=FALSE}
#Change factors to integers
TAM3_CF <- lapply(TAM3_CF, as.numeric)

#verify negative statements changed correctly
head(TAM3_CF$PEC4)
head(TAM3_CF$RES4)
head(TAM3_CF$CPLAY4)
head(TAM3_CF$CANX1)

#Put back as dataframe
TAM3_CF <- data.frame(TAM3_CF)

#Check how many NAs per observation
#25 people missed at least one response. 
#7 people missed 4 or more responses
rowSums(is.na(TAM3_CF))


#Listwise deletion for rows with more than 3 NAs. 
TAM3_CF_CLEAN <- TAM3_CF[rowSums(is.na(TAM3_CF)) <= 3, ] 
#Down to 86 observations (from 93) after deletion of rows with more than 3 NAs

#Check the number of NAs
#105 NAs before NA removal
table(is.na(TAM3_CF))
#30 NAs after NA removal
table(is.na(TAM3_CF_CLEAN))

#Imputation is unneeded since composite scores will be completed. NAs will be removed from an individuals composite variable score. 

str(TAM3_CF_CLEAN)
summary(TAM3_CF_CLEAN)
```

## Mean Composites for Constructs

A mean composite was computed to represent each construct based on the survey data. 

```{r Construct Scores, echo=FALSE}
TAM3_CF_CLEAN$USE_COMP <- apply(TAM3_CF_CLEAN[ ,1:7], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$BI_COMP <- apply(TAM3_CF_CLEAN[ ,8:15], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$PEU_COMP <- apply(TAM3_CF_CLEAN[ ,16:19], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$PU_COMP <- apply(TAM3_CF_CLEAN[ ,20:23], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$CSE_COMP <- apply(TAM3_CF_CLEAN[ ,24:27], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$PEC_COMP <- apply(TAM3_CF_CLEAN[ ,28:31], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$ENJ_COMP <- apply(TAM3_CF_CLEAN[ ,32:34], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$SN_COMP <- apply(TAM3_CF_CLEAN[ ,35:38], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$IMG_COMP <- apply(TAM3_CF_CLEAN[ ,39:41], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$REL_COMP <- apply(TAM3_CF_CLEAN[ ,42:44], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$OUT_COMP <- apply(TAM3_CF_CLEAN[ ,45:47], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$RES_COMP <- apply(TAM3_CF_CLEAN[ ,48:51], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$VOL_COMP <- apply(TAM3_CF_CLEAN[ ,52:54], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$CPLAY_COMP <- apply(TAM3_CF_CLEAN[ ,55:58], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$CANX_COMP <- apply(TAM3_CF_CLEAN[ ,59:62], MARGIN = 1, mean, na.rm=TRUE)
TAM3_CF_CLEAN$CF_COMP <- apply(TAM3_CF_CLEAN[ ,63:68], MARGIN = 1, mean, na.rm=TRUE)

TAM3_CF_COMP <- TAM3_CF_CLEAN[,c(69:84)]
summary(TAM3_CF_COMP)

TAM3_CF_COMP %>% 
  gather(key="MesureType", value="Val") %>%
  ggplot( aes(x=MesureType, y=Val, fill=MesureType)) +
    geom_violin()

#ggsave("Comp.png", width = 10, height = 5)
```

#Reliability Testing
```{r Cronbach Alpha Tests, echo=FALSE}

#install.packages("psy")
library(psy)

CR_USE <- cronbach(TAM3_CF_CLEAN[,1:7])
print(CR_USE)
CR_BI <- cronbach(TAM3_CF_CLEAN[,8:15])
print(CR_BI)
CR_PEU <- cronbach(TAM3_CF_CLEAN[,16:19])
print(CR_PEU)
CR_PU <- cronbach(TAM3_CF_CLEAN[,20:23])
print(CR_PU)
CR_CSE <- cronbach(TAM3_CF_CLEAN[,24:27])
print(CR_CSE)
CR_PEC <- cronbach(TAM3_CF_CLEAN[,28:31])
print(CR_PEC)
CR_ENJ <- cronbach(TAM3_CF_CLEAN[,32:34])
print(CR_ENJ)
CR_SN <- cronbach(TAM3_CF_CLEAN[,35:38])
print(CR_SN)
CR_IMG <- cronbach(TAM3_CF_CLEAN[,39:41])
print(CR_IMG)
CR_REL <- cronbach(TAM3_CF_CLEAN[,42:44])
print(CR_REL)
CR_OUT <- cronbach(TAM3_CF_CLEAN[,45:47])
print(CR_OUT)
CR_RES <- cronbach(TAM3_CF_CLEAN[,48:51])
print(CR_RES)
CR_VOL <- cronbach(TAM3_CF_CLEAN[,52:54])
print(CR_VOL)
CR_CPLAY <- cronbach(TAM3_CF_CLEAN[,55:58])
print(CR_CPLAY)
CR_CANX <- cronbach(TAM3_CF_CLEAN[,59:62])
print(CR_CANX)
CR_CF <- cronbach(TAM3_CF_CLEAN[,63:68])

```
#Descriptive Statistics

```{r Descriptive Stats, echo=TRUE}

library(psych)
corr.test(TAM3_CF_COMP)
cov(TAM3_CF_COMP)

library(reshape2)
TAM3_COR <- round(cor(TAM3_CF_COMP), 2)
print(TAM3_COR)
MELT_TAM3_COR <- melt(TAM3_COR)
head(TAM3_COR)

ggplot(data = MELT_TAM3_COR, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
describe(TAM3_CF_COMP)


install.packages("Hmisc")
library(Hmisc)
CORR_DATA <- rcorr(as.matrix(TAM3_CF_COMP))

library(ggcorrplot)
heatmap <- ggcorrplot(TAM3_COR, hc.order = TRUE, type = "lower",
            outline.col = "white",
            ggtheme = ggplot2::theme_gray,
            colors = c("#6D9EC1", "white", "#E46726"))

print(heatmap)
print(CORR_DATA)
#ggsave("heatmap.png")

```










